%===================================================================================================
\section{Model Structure \& Notation}\label{mod.str}
The model aims to capture heterosexual HIV transmission among the Swati population aged 15--49.
The modelled population is stratified along five dimensions
(Table~\ref{tab:model.dims} and Figure~\ref{fig:model}), including:
2 sexes~($s$), 4 activity groups~($i$), 6 HIV states~($h$), and 5 cascade states~($c$);
the fifth dimension tracks seroconcordant HIV+ partnerships
and includes strata for each of 4 partnership types ($p$) plus 1 extra stratum
--- see \sref{foi.prop} for full details.
In total, $2 \cdot 4 \cdot (1 + 5 \cdot 5 \cdot 5) = 1008$ states are modelled,
since the cascade and partnership dimensions are only applicable to people living with HIV ($h>1$).
Two types of sex acts ($a$) are also considered.
\begin{table}[h]
  \centering
  \caption{Overview of model dimensions and stratifications}
  \label{tab:model.dims}
  \input{\app/tab.dims}
  \floatfoot{See footnote \ref{foot:code.note} regarding indices in the code.}
\end{table}
\ifappfigmodel\input{\app/fig.model}\fi
%---------------------------------------------------------------------------------------------------
\paragraph{Sexual Activity}
Sexual activity groups were defined to reflect common stratifications in the available data,
and persistent differences in HIV incidence and prevalence
\cite{SDHS2006,Bicego2013,Justman2016,SHIMS2}.
The lowest sexual activity group ($i=1$) comprises
individuals who had 0-1 sexual partners in the past 12 months (p12m),
but did not engage in sex work.
The medium activity group ($i=2$) similarly comprises
individuals who had 2+ sexual partners in p12m
but did not engage in formal sex work.
The highest two activity groups among women ($i=3,4$) comprise
lower and higher risk FSW (see \sref{mod.par.fsw} for more details), and
the highest two activity groups among men ($i=3,4$) likewise comprise
lower and higher risk clients of FSW.
%---------------------------------------------------------------------------------------------------
\paragraph{Partnership Types}
Four types of sexual partnerships are modelled,
capturing differences in partnership durations, and
trends in condom use relevant to inferred transmission dynamics.
The four partnership types are:
long-term/spousal partnerships ($p=1$, lowest condom use, long duration);
short-term partnerships ($p=2$, medium condom use, medium duration);
one-off/occasional sex work partnerships ($p=3$, highest condom use, 1 sex act);
and repeat/regular sex work partnerships ($p=4$, medium condom use, medium duration).
Figure~\ref{fig:model.risk} illustrates
the modelled activity groups and possible partnership types between them.
%---------------------------------------------------------------------------------------------------
\paragraph{HIV Infection \& Treatment}
HIV infection is stratified into
acute-HIV and stages defined by CD4 count (Figure~\ref{fig:model.hiv})
to reflect changes in mortality~\cite{Mangal2017},
historical ART eligibility~\cite{EswMOH2006gui,EswMOH2010gui,EswMOH2015gui,EswMOH2018gui},
and, with CD4 as a proxy for viral load, infectiousness~\cite{Boily2009}.
The modelled ART cascade (Figure~\ref{fig:model.cascade})
includes the steps associated with the ``90-90-90'' targets,
plus a generic ``virally un-suppressed'' state reflecting any combination of
treatment failure, discontinuation, or loss to follow-up after achieving viral suppression.
Loss to follow-up prior to viral suppression is not explicitly modelled,
but subsumed into rates of ART initiation and viral suppression.
